Simulation_Study

### 2022-03-07 Simulation_Study.Rmd
Plots for Simulation

>>>>

```{r functions, echo = False}
n_constant_l.data <- data.frame(

   n = c(),
   ar = c(),
   sigma = c(),
   l = c(),
   mean = c(), 
   nm_se = c(),
   nm_lower = c(), 
   nm_upper = c(),
   nm_success = c(),
   mv_se = c(),
   mv_lower = c(), 
   mv_upper = c(),
   mv_success = c(),
   true_se = c(),
   nm_diff = c(),
   mv_diff = c(),
   nm_percent_change = c(),
   mv_percent_change = c()
)

for(n in c(50, 100, 150, 200, 250, 300, 350, 400, 450, 500, 550, 600, 650, 700, 750, 800, 850, 900, 950, 1000))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.5, 0.1, 10, m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.5),
     sigma = c(0.1),
     l = c(10),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_change = c(m[13]),
     mv_percent_change = c(m[14])
    )
    n_constant_l.data = rbind(n_constant_l.data, tobind.data)
  }
}

print(n_constant_l.data)
```

```{r functions, echo = False}

plot(n_constant_l.data$n, n_constant_l.data$nm_success, pch = 19, col = rgb(red = 0.2, green = 0.2, blue = 0.2, alpha = 0.3))
```

```{r functions, echo = False}

plot(n_constant_l.data$n, n_constant_l.data$mv_success, pch = 19, col = rgb(red = 0.2, green = 0.2, blue = 0.2, alpha = 0.3))
```

```{r functions, echo = False}

plot(n_constant_l.data$n, n_constant_l.data$nm_diff, pch = 19, col = rgb(red = 0.2, green = 0.2, blue = 0.2, alpha = 0.3))
```

```{r functions, echo = False}

plot(n_constant_l.data$n, n_constant_l.data$mv_diff, pch = 19, col = rgb(red = 0.2, green = 0.2, blue = 0.2, alpha = 0.3))
```

```{r functions, echo = False}

plot(n_constant_l.data$n, n_constant_l.data$nm_percent_change, pch = 19, col = rgb(red = 0.2, green = 0.2, blue = 0.2, alpha = 0.3))
```

```{r functions, echo = False}

plot(n_constant_l.data$n, n_constant_l.data$mv_percent_change, pch = 19, col = rgb(red = 0.2, green = 0.2, blue = 0.2, alpha = 0.3))
```

```{r functions, echo = False}

plot(n_constant_l.data$n, n_constant_l.data$mv_percent_change, pch = 19, col = rgb(red = 0.2, green = 0.2, blue = 0.2, alpha = 0.3))
```
